### 2020-08-25 manuscript/PLOS-MSc-Thesis.tex
change first paragraph of abstract according to J. Gutiérrez recomendations

\subsection*{Background}
One of the central problems in developmental and synthetic biology is to 
understand how cells process external cues on its relative position to other 
cells in a developing embryo, a tissue or in a petri dish and transform such
information into a coherent response, e.g. terminal differentiation state. It 
has been stated that a gradient of concentration of certain molecule is enough 
to provide such positional information and produce cell differentiation by 
interacting with the cell's gene regulatory networks (GRNs).

>>>>

\subsection*{Background}
A central problem in developmental and synthetic biology is to understand the 
mechanisms by which cells in a tissue or in a petri dish process external cues 
and transform such information into a coherent response, e.g. a terminal 
differentiation state. It has been stated that a gradient of concentration of 
certain molecule is enough to provide such positional information and produce 
cell differentiation by interacting with the cell's gene regulatory networks 
(GRNs).
